Model Checking Differentially Private Properties

### 2018-01-28 applications.tex
add more descriptions

Based on the density estimation algorithm in \cite{DNPRY:10:PPSA}, we
consider the following mechanism for event type streams. Our mechanism
keeps a flag for each event type.

>>>>

Based on the density estimation algorithm in \cite{DNPRY:10:PPSA}, we
consider the following mechanism for event type streams. Our mechanism
keeps a flag for each event type. The flags are initialized to $0$ or
$1$ uniformly. On observing an event type in the input stream, the
flag for the event type is set to $0$ and $1$ with probability
$\frac{3}{8}$ and $\frac{5}{8}$ respectively. The mechanism continues
to update its flags until it is asked to return the number of observed
event types.
